Implementation of a Fuzzy Rule-Based Classifier using Genetic Algorithms

### 2017-12-02 Article/article.tex
GAA and classifier : slight modifications Article : Adding section 6 -> fitness function

>>>>

\section{Compute the fitness function}

The calculation of the fitness function is the core of our implementation.\\
We will be trying to explain in depth the structure of that function.

\subsection{Vector of best class confidence}

Given a rule, we measure the truth degree of that rule using the formula previously described on our training data for each class.
The function \textit{getConf} gives the vector :

\[
\begin{bmatrix}
C_1:\mu_b^1(r)\\
C_2:\mu_b^2(r)\\
C_3:\mu_b^3(r)
\end{bmatrix} \]

with $C_i$ the class and $\mu_b^i(r)$ the truth degree of that rule $r$ on class $i$.
\\
\\
An Individual is composed by a set of rules, so the function \textit{getConfVect} gives the vector :
\[
\vec{Conf}=
\begin{bmatrix}
C_i^1:\mu_b^i(r_1)\\
C_i^2:\mu_b^i(r_2)\\
\vdots\\
C_i^m:\mu_b^i(r_m)\\
\end{bmatrix} \]
With $m$ the number of rules. For each rule, we take the maximum $\mu_b$ from \textit{getConf}. This vector represents for each rule fo an individual, what class it fits the better, and with which confidence.

\subsection{Vector of $\mu_A$, given a data instance and rules}

The next step is to do fuzzy composition on each of the rule, given an instance of data, here $[x_1,x_2,x_3,x_4]$.

The function \textit{getMuA} takes two parameters: a data instance and a rule.

Remembering this formula:
\[A=[x_{p(1)}=\bigcup_{j\in D(1)}A(p(1),j) ] \bigcap\cdots\bigcap[x_{p(s)}=\bigcup_{j\in D(s)}A(p(s),j)]\]

We chose to measure $\mu_a$ like this:

\[\mu_A=
min
\begin{pmatrix}
max(A(p(1),j),\forall j \in D(1))\\
\vdots \\
max(A(p(s),j),\forall j \in D(s))
\end{pmatrix}
    \]
\textbf{Example:}\\
\\
Let take our example rule:
\begin{center}
If Sepal Length is Small AND Sepal Width is Medium OR Big AND Petal Width is Small OR Medium OR Big
\end{center}
And a data instance (normalized): $x_1=0.97,x_2=0.86,x_3=0.97,x_4=0.88$.\\
\[
\begin{split}
\mu_A &= min
\begin{pmatrix}
max(\mu_S(0.97))\\
max(\mu_M(0.86),\mu_B(0.86))\\
max(\mu_S(0.88),\mu_M(0.88),\mu_B(0.88))
\end{pmatrix}\\
&= min
\begin{pmatrix}
max(0)\\
max(0.28,0.72)\\
max(0,0.24,0.76)
\end{pmatrix}\\
&= min(0,0.72,0.76) = 0
\end{split}
\]
\\
\begin{center} \rule[1ex]{.5\textwidth}{.5pt} \end{center}
\newpage

In the same fashion as we did for our confidence vector, we use the function \textit{getMuVect}:

\[
\vec{\mu_A^k}=
\begin{pmatrix}
\mu_A^k(r_1)\\
\vdots\\
\mu_A^k(r_m)
\end{pmatrix}
\]
For the k-th piece of data from the test data.

\subsection{Assembling the pieces: predicting a class}

We want now to get the predicted confidence of classes for an instance.\\
$\vec{Conf}$ gives us the fittest class for each rule, and $\vec{\mu_A}$ its confidence given an instance of data. \\
There is several way to compute the class predicted using these vectors.
\\
\\
\textbf{Simple method:}
\\
For each class, we take the average of $\mu_A$ for every rule that have that class as the highest truth degree:
\[
\text{Predicted Classes Confidence: }
\begin{pmatrix}
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_1\\
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_2\\
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_3
\end{pmatrix}
\]
Here, the class predicted will simply be the maximum average.

\subsection{Accuracy \& Fitness function}

The accuracy gives us the percentage of well predicted instances of our classification on a test data. We can use only this score as a fitness function.\\
It seems that using the training data to define the truth degree, then applying the simple method is already a good way to classify.\\
When taking the average of the average accuracy of 20 populations of 20 randomly generated individuals, we have a 0.77 accuracy.\\
And when taking the average accuracy of the fittest individual of 20 random populations, we get a 0.96 accuracy.\\
Decision Tree Classifier is a similar method with crisp rules. The accuracy of that method is 0.92 on the same dataset.\\
However, accuracy score is not our only concern : we would like to have the fewest rules as possible, as we want to produce a clear and simple rule system if one exists. So we have to compute a fitness function combining both the accuracy score and the complexity of the ruleset.
